### 2014-08-31 fundamentals/intro.tex
adds Cyclus smallcaps command

The Cyclus code arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.

\subsection{Motivation}
% Gently reiterate the above need. 
% There should be a hero narrative here
% There was a gap in the capabilities of simulators.
% Cyclus, a hero, came in to fill that gap.

% MJG - @gonuke has always cited method-to-method comparisons as the primary
% benefit Cyclus can bring to the table. Do we want to frame the hero narrative
% in that context? The more I think about, the more I feel like this is a
% secondary argument. I'll take a crack at a few sentences below.

In addition to providing the fundamental features expected in fuel cycle 
simulators, the Cyclus paradigm enables two major capabilites that previous 
simulators were lacking. First, it enables simulations at multiple levels of 
fidelity.  It also facilitates direct comparison of modeling methodologies.

@@

Cyclus uses a divide-and-conquer approach, separating the problem of modeling a
physics-dependent supply chain into a simulation kernel and archetypes that
interact with the kernel during a simulation. The kernel is responsible for the
deployment and interaction logic of entities in the simulation. Physics
calculations are constrained to individual archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle, e.g. reprocessing and advance
fuel fabrication, rather than also modeling the entirety of the cycle.

% we could use a specific example of Cosi's equivalence method below
Because Cyclus uses a modular archetype approach, comparing two archetypes is
straightforward. Consider a case in which an analyst would like to compare the
effect of using different models to determining input fuel composition for fast
reactors. A variety fuel fabrication archetypes can be developed and used
interchangably to analyze the effect of each on a simulation's output.

@@

We expect that there are a number of types of users and developers who will 
interact with the Cyclus framework. Those people fall into a number of 
categories. All such people benefit from the modular architecture.

% man that figure has gone quite a ways =)
<modified-open-source collaboration diagram>

>>>>

The \Cyclus code arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.

\subsection{Motivation}
% Gently reiterate the above need. 
% There should be a hero narrative here
% There was a gap in the capabilities of simulators.
% \Cyclus, a hero, came in to fill that gap.

% MJG - @gonuke has always cited method-to-method comparisons as the primary
% benefit \Cyclus can bring to the table. Do we want to frame the hero narrative
% in that context? The more I think about, the more I feel like this is a
% secondary argument. I'll take a crack at a few sentences below.

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables two major capabilites that previous 
simulators were lacking. First, it enables simulations at multiple levels of 
fidelity. Second, it facilitates direct comparison of modeling methodologies.

@@

\Cyclus separates the problem of modeling a
physics-dependent supply chain into a simulation kernel and archetypes that
interact with the kernel during a simulation. The kernel is responsible for the
deployment and interaction logic of entities in the simulation. Physics
calculations are constrained to individual archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle, e.g. reprocessing and advance
fuel fabrication, rather than also modeling the entirety of the cycle.

% we could use a specific example of Cosi's equivalence method below
Because \Cyclus uses a modular archetype approach, comparing two archetypes is
straightforward. Consider a case in which an analyst would like to compare the
effect of using different models to determining input fuel composition for fast
reactors. A variety fuel fabrication archetypes can be developed and used
interchangably to analyze the effect of each on a simulation's output.

@@

We expect that there are a number of types of users and developers who will 
interact with the \Cyclus framework. Those people fall into a number of 
categories. All such people benefit from the modular architecture.

\begin{figure}[htbp!]
\begin{center}
\includegraphics{modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully 
closed collaborations.}
\label{fig:modifiedopen}
\end{figure}
